Add Plant Functional Type labels

### 2021-03-09 R/add_plant_functional_type.Rmd
exploring packages for PFT labels

```{r install_load_packages, message=FALSE}
#install.packages("request")
#library(devtools)
#devtools::install_github("sckott/request")
library('request')
library('tibble')
```

@@

@@

Let’s say we’re interested in the species Xanthium strumarium and we’d like some occurrence data.

```{r}
Xanthium_strumarium <- BIEN_occurrence_species(species = "Xanthium strumarium")
#View(Xanthium_strumarium)
head(Xanthium_strumarium)
str(Xanthium_strumarium)
```
The default data that is returned consists of the latitude, longitude and date collected, along with a set of attribution data. If we want more information on these occurrences, we just need to change the arguments:

```{r}
Xanthium_strumarium_full <- BIEN_occurrence_species(species = "Xanthium strumarium",cultivated = T,only.new.world = T,all.taxonomy = T,native.status = T,observation.type = T,political.boundaries = T)

str(Xanthium_strumarium_full)
```

Let’s take a quick look at where those occurrences are.

```{r}
# Make a quick map to plot our points on
map('world',fill=T , col= "grey", bg="light blue")

# Plot the points from the full query in red
points(cbind(Xanthium_strumarium_full$longitude,Xanthium_strumarium_full$latitude),col="red",pch=20,cex=1)

# Plot the points from the default query in blue
points(cbind(Xanthium_strumarium$longitude,Xanthium_strumarium$latitude),col="blue",pch=20,cex=1) 
```

@@

Let’s say we’re interested in the genus Abies, and we’d like to get an idea of how many species there are in this genus and what higher taxa it falls within.

>>>>

```{r install_load_packages, message=FALSE}
#install.packages("request")
#library(devtools)
#devtools::install_github("sckott/request")
library(request)
library(tibble)
library(tidyverse)
library(here)
```

@@

Based on the GitHub issue discussion (https://github.com/USDA/USDA-APIs/issues/7), someone uploaded USDA plants data here from 2016: https://uofi.app.box.com/v/usdaplants

```{r, eval=FALSE, include=FALSE}
# Specify URL where file is stored 
url <- "https://uofi.app.box.com/v/usdaplants/folder/6688524249/usda_plants_20160713.csv"
destFile <- file.path(here::here(), "analysis","data", "usda_plants_20160713.csv")
# Apply download.file function in R
download.file(url, destFile)
```

```{r}
#usda_plants <- read_csv(file.path(here::here(), "analysis", "data", "usda_plants_20160713.csv"),
                        local = locale(encoding = "latin1"))

# Error in nchar(x) : invalid multibyte string, element 2
# ^ Issue with some of the column names in the .csv? 
```

@@

"Let’s say we’re interested in the species Xanthium strumarium and we’d like some occurrence data."

```{r}
Xanthium_strumarium <- BIEN_occurrence_species(species = "Xanthium strumarium")
#View(Xanthium_strumarium)
head(Xanthium_strumarium)
str(Xanthium_strumarium)
```

@@

"Let’s say we’re interested in the genus [Abies], and we’d like to get an idea of how many species there are in this genus and what higher taxa it falls within."
